Post-Disturbance Tree Community Trajectories in a Neotropical Forest

### 2018-06-04 WholePlotTrajectories.Rmd
pdf

  To disentangle the ecological processes driving forests dynamics we examined the the trajectories over 30 years after a gradient of logging and thinning disturbance, focusing on communities taxonomic and functional composition and diversity.
  Specifically we analysed the trajectories of communities taxonomic richness and evennes and functional composition, diversity and redundancy based on 7 key functional traits assessing species ecology.

  We highlighted a decoupling between functional and taxonomic trajectories, translating a fast recovery of communities functioning while their taxonomic recovery was slowed by the recruitment of infrequent species specific to mature forests.
  The IDH consistently predicted communities functional trajectories but poorly reflected the taxonomic ones, blurried by changes in the functional redundancy entailing competitive exclusion.
  Although communities consistently recovered their functioning after 30 years, initially infrequent species proved long to recover which impacted the taxonomic structure and functoinal redundancy over several decades.
  Our results acknowledged the need of decades-long recovery cycles to restore the resilience of the community and prevent species loss in the long term.

keywords: [Taxonomic and Functional Biodiversity, Neotropical Forests, Disturbance Trajectories, Intermediate Disturbance Hypothesis, Long-term Resilience]
journalinfo: Hal xxx
archive: DOI xxxx
date: "`r format(Sys.time(), '%d %B %Y')`"
preamble: >
  \usepackage{textcomp}
  \DeclareUnicodeCharacter{B0}{\textdegree}
  \usepackage{tabu}
  \usepackage{caption}
  \captionsetup{justification = justified}
  \renewenvironment{table}{\begin{table*}}{\end{table*}\ignorespacesafterend}
  \hyphenation{bio-di-ver-si-ty sap-lings}
bibliography: references.bib
lang: english
keywordlabel: Keywords
corrauthorlabel: Corresponding author
output:
  bookdown::gitbook: default
  bookdown::pdf_book:
    base_format: EcoFoG::article
    keep_tex: TRUE
  bookdown::word_document2: default
---

>>>>

    To disentangle the ecological processes driving forests dynamics we examined the the trajectories over 30 years after a gradient of logging and thinning disturbance, focusing on communities taxonomic and functional composition and diversity.
    Specifically we analysed the trajectories of communities taxonomic richness and evennes and functional composition, diversity and redundancy based on 7 key functional traits assessing species ecology.
    We highlighted a decoupling between functional and taxonomic trajectories, translating a fast recovery of communities functioning while their taxonomic recovery was slowed by the recruitment of infrequent species specific to mature forests.
    The IDH consistently predicted communities functional trajectories but poorly reflected the taxonomic ones, blurried by changes in the functional redundancy entailing competitive exclusion.
    Although communities consistently recovered their functioning after 30 years, initially infrequent species proved long to recover which impacted the taxonomic structure and functoinal redundancy over several decades.
    Our results acknowledged the need of decades-long recovery cycles to restore the resilience of the community and prevent species loss in the long term.

keywords: [Taxonomic and Functional Biodiversity, Neotropical Forests, Disturbance Trajectories, Intermediate Disturbance Hypothesis, Long-term Resilience]
journalinfo: Hal xxx
archive: DOI xxxx
date: "`r format(Sys.time(), '%d %B %Y')`"
preamble: >
  \usepackage{textcomp}
  \DeclareUnicodeCharacter{B0}{\textdegree}
  \usepackage{tabu}
  \usepackage{caption}
  \captionsetup{justification = justified}
  \renewenvironment{table}{\begin{table*}}{\end{table*}\ignorespacesafterend}
  \hyphenation{bio-di-ver-si-ty sap-lings}
bibliography: references.bib
lang: english
keywordlabel: Keywords
corrauthorlabel: Corresponding author
output:
  bookdown::pdf_book:
    base_format: EcoFoG::article
    keep_tex: TRUE
  bookdown::gitbook: default
  bookdown::word_document2: default
---

### 2018-06-04 WholePlotTrajectories.tex
pdf

\Abstract{
Understand the maintenance of forests biodiversity structure,
functioning and dynamics is urgent to anticipate their fate in the
global changing context. Communities diversity structure is assumed to
rely on a constant regime of disturbance and peak at intermediate
intensity. For tropical forests this intermediate disturbance hypothesis
(IDH) remain debated as well as the completeness of forests resilience
in all taxonomic and functional facets.
}

>>>>

\Abstract{
Understand the maintenance of forests biodiversity structure,
functioning and dynamics is urgent to anticipate their fate in the
global changing context. Communities diversity structure is assumed to
rely on a constant regime of disturbance and peak at intermediate
intensity. For tropical forests this intermediate disturbance hypothesis
(IDH) remain debated as well as the completeness of forests resilience
in all taxonomic and functoinal facets. To disentangle the ecological
processes driving forests dynamics we examined the the trajectories over
30 years after a gradient of logging and thinning disturbance, focusing
on communities taxonomic and functional composition and diversity.
Specifically we analysed the trajectories of communities taxonomic
richness and evennes and functional composition, diversity and
redundancy based on 7 key functional traits assessing species ecology.
We highlighted a decoupling between functional and taxonomic
trajectories, translating a fast recovery of communities functioning
while their taxonomic recovery was slowed by the recruitment of
infrequent species specific to mature forests. The IDH consistently
predicted communities functional trajectories but poorly reflected the
taxonomic ones, blurried by changes in the functional redundancy
entailing competitive exclusion. Although communities consistently
recovered their functioning after 30 years, initially infrequent species
proved long to recover which impacted the taxonomic structure and
functoinal redundancy over several decades. Our results acknowledged the
need of decades-long recovery cycles to restore the resilience of the
community and prevent species loss in the long term.
}
